\documentclass[14pt,a4paper]{extarticle}

\input{preamble.tex}

\def\musicmode{1}
\definecolor{chordColor}{HTML}{

\cfoot{}    % Remove footer


\begin{document}

\begin{song}{Across The Lands}
  \verse
  {You're the \m{C}Word of \m{G}God the \m{F}Father,}
  {From be\m{F}fore the \m{G}world began;}
  {Every \m{F}star and every \m{C}planet}
  {Has been \m{Dm}fashioned by Your \m{F}hand.}
  {All cre\m{C}ation \m{G}holds to\m{F}gether}
  {By the \m{C}power \m{G}of Your voice}
  {Let the \m{F}skies declare Your \m{C}glory}
  {Let the \m{Dm}land and \m{F}seas re\m{G}joice!}
  \end
  \chorus
  {You're the \m{F}Author of cre\m{C}ation,}
  {You're the \m{F}Lord of \m{G}every \m{Am}man;}
  {And Your \m{F}cry of love rings \m{Am}out}
  {A\m{G}cross the \m{C}lands.}
  \end
  \verse
  {Yet You left the gaze of angels,}
  {Came to seek and save the lost,}
  {And exchanged the joy of Heaven}
  {For the anguish of a cross.}
  {With a prayer you fed the hungry,}
  {With a word You stilled the sea.}
  {Yet how silently You suffered}
  {That the guilty may go free.}
  \end
  \verse
  {With a shout You rose victorious,}
  {Wrestling victory from the grave,}
  {And ascended into Heaven}
  {Leading captives in Your wake.}
  {Now You stand before the Father}
  {Interceding for Your own;}
  {From each tribe and tongue and nation,}
  {You are leading sinners home!}
  \end
\end{song}
\pagebreak
\begin{song}{It Is Well}
  \verse
  {When \m{B{\flat}}peace, like a \m{Gm}river, a\m{E{\flat}}tten\m{F}deth my \m{B{\flat}}way,}
  {\m{F}When \m{Gm}sorrows like \m{C}sea billows \m{F}roll;}
  {\m{F}What\m{B{\flat}}ever my \m{E{\flat}}lot, Thou hast \m{C}taught me to \m{F}say,}
  {It is \m{B{\flat}}well, it is \m{E{\flat}}well \m{F}with \m{B{\flat}}my soul.}
  \end
  \chorus
  {\m{B{\flat}}It is well (\m{B{\flat}}it is \m{F}well)}
  {\m{B{\flat}}With my soul (\m{F}with \m{F7}my \m{B{\flat}}soul)}
  {\m{B{\flat}}It is \m{E{\flat}}well, it is \m{B{\flat}}well \m{F}with \m{B{\flat}}my soul.}
  \end
  \verse
  {Though Satan should buffet, though trials should come,}
  {Let this blest assurance control,}
  {That Christ hath regarded my helpless estate,}
  {And hath shed His own blood for my soul.}
  \end
  \verse
  {My sin -- Oh, the bliss of this glorious thought! --}
  {My sin, not in part but the whole,}
  {Is nailed to the cross, and I bear it no more,}
  {Praise the Lord, praise the Lord, O my soul!}
  \end
  \verse
  {And Lord, haste the day when the faith shall be sight,}
  {The clouds be rolled back as a scroll;}
  {The trump shall resound, and the Lord shall descend,}
  {Even so, it is well with my soul.}
  \end
\end{song}
\pagebreak
\begin{song}{In Christ Alone}
  \verse
  {In \m{G}Christ \m{D}alone my \m{G}hope is \m{A}found,}
  {\m{D}He is my \m{G}light, my \m{A}strength, my \m{D}song;}
  {This \m{G}Corner\m{D}stone, this \m{G}solid \m{A}Ground,}
  {\m{D}Firm through the \m{G}fiercest \m{A}drought and \m{D}storm.}
  {\m{D}What Heights of \m{G}love, what \m{D}depths of \m{A}peace,}
  {When \m{D}fears are \m{G}stilled, when \m{Bm}strivings \m{A}cease!}
  {My \m{G}Comfor\m{D}ter, my \m{G}All in \m{A}All,}
  {\m{D}Here in the \m{G}love of \m{A}Christ I \m{D}stand.}
  \end
  \verse
  {In Christ alone! – who took on flesh,}
  {Fullness of God in helpless babe.}
  {This gift of love and righteousness,}
  {Scorned by the ones He came to save:}
  {Till on the cross as Jesus died,}
  {The wrath of God was satisfied-}
  {For every sin on His was laid;}
  {Here in the death of Christ I live.}
  \end
  \verse
  {There in the ground His body lay,}
  {Light of the world by darkness slain:}
  {Then bursting forth in glorious day}
  {Up from the grave He rose again!}
  {And as He stand in victory}
  {Sin's curse has lost its grip on me,}
  {For I am His and He is mine-}
  {Bought with the precious blood of Christ.}
  \end
  \verse
  {No guilt in life, no fear in death,}
  {This is the power of Christ in me;}
  {From life's first cry to final breath,}
  {Jesus commands my destiny.}
  {No power of Hell, no scheme of man,}
  {Can ever pluck me from His hand:}
  {Till He returns or calls me home,}
  {Here in the power of Christ I stand.}
  \end
\end{song}
\pagebreak
\begin{song}{I Heard The Voice Of Jesus Say}
  \verse
  {I \m{C{\sharp}m}heard the voice of \m{E}Jesus \m{B}say,}
  {“Come \m{C{\sharp}m}unto \m{A}Me and \m{B}rest;}
  {Lay \m{C{\sharp}m}down, thou weary \m{E}one, lay \m{B}down}
  {Thy \m{C{\sharp}m}head \m{B}upon My \m{C{\sharp}m}breast.”}
  {I \m{E}came to Jesus \m{B}as I \m{C{\sharp}m}was,}
  {So \m{E}weary, \m{F{\sharp}m}worn and \m{G{\sharp}m}sad;}
  {I \m{C{\sharp}m}found in Him a \m{E}resting \m{B}place,}
  {And \m{G{\sharp}}He has \m{F{\sharp}m}made me \m{C{\sharp}m}glad.}
  \end
  \verse
  {I heard the voice of Jesus say,}
  {“Behold, I freely give}
  {The living water; thirsty one,}
  {Stoop down, and drink, and live.”}
  {I came to Jesus, and I drank}
  {Of that life-giving stream;}
  {My thirst was quenched, my soul revived,}
  {And now I live in Him.}
  \end
  \verse
  {I heard the voice of Jesus say,}
  {“I am this dark world's Light;}
  {Look unto Me, thy morn shall rise,}
  {And all thy day be bright.”}
  {I looked to Jesus, and I found}
  {In Him my Star, my Sun;}
  {And in that light of life I'll walk,}
  {Till trav'ling days are done.}
  \end
  \verse
  {I heard the voice of Jesus say,}
  {“My Father's house above}
  {Has many mansions; I've a place}
  {Prepared for you in love.”}
  {I trust in Jesus—in that house,}
  {According to His word,}
  {Redeemed by grace, my soul shall live}
  {Forever with the Lord.}
  \end
\end{song}

\end{document}
