\begin{psalm}{Psalm 51 \tr}{C.M.}
  \verse
  {\textsuperscript{1} After thy loving-kindness, Lord,}
  {have mercy upon me:}
  {For thy compassions great, blot out}
  {all mine iniquity.}
  \end
  \verse
  {\textsuperscript{2} Me cleanse from sin, and throughly wash}
  {from mine iniquity:}
  {\textsuperscript{3} For my transgressions I confess;}
  {my sin I ever see.}
  \end
  \verse
  {\textsuperscript{4} `Gainst thee, thee only, have I sinned,}
  {in thy sight done this ill;}
  {That when thou speak'st thou may'st be just,}
  {and clear in judging still.}
  \end
  \verse
  {\textsuperscript{5} Behold, I in iniquity}
  {was formed the womb within;}
  {My mother also me conceived}
  {in guiltiness and sin.}
  \end
  \verse
  {\textsuperscript{6} Behold, thou in the inward parts}
  {with truth delighted art;}
  {And wisdom thou shalt make me know}
  {within the hidden part.}
  \end
  \verse
  {\textsuperscript{7} Do thou with hyssop sprinkle me,}
  {I shall be cleans\'ed so;}
  {Yea, wash thou me, and then I shall}
  {be whiter than the snow.}
  \end
  \verse
  {\textsuperscript{8} Of gladness and of joyfulness}
  {make me to hear the voice;}
  {That so these very bones which thou}
  {hast broken may rejoice.}
  \end
  \verse
  {\textsuperscript{9} All mine iniquities blot out,}
  {thy face hide from my sin.}
  {\textsuperscript{10} Create a clean heart, Lord, renew}
  {a right \underline{spirit} me within.}
  \end
  \verse
  {\textsuperscript{11} Cast me not from thy sight, nor take}
  {thy Holy \underline{Spirit} away.}
  {\textsuperscript{12} Restore me thy salvation's joy;}
  {with thy free \underline{Spirit} me stay.}
  \end
\end{psalm}

% ---

