\begin{psalm}{Psalm 103 \sp}{D.L.M.}
  \verse
  {\textsuperscript{1} Praise God, my soul! With all my heart}
  {Let me exalt his holy name.}
  {\textsuperscript{2} Forget not all his benefits;}
  {His praise, my soul, in song proclaim.}
  {\textsuperscript{3} The {\LORD} forgives you all your sins,}
  {And heals your sickness and distress;}
  {\textsuperscript{4} Your life he rescues from the grave,}
  {And crowns you in his tenderness.}
  \end
  \verse
  {\textsuperscript{5} He satisfies your deep desires}
  {From his unending stores of good,}
  {So that, just like the eagle's strength,}
  {Your youthful vigour is renewed.}
  {\textsuperscript{6} The {\LORD} is known for righteous acts}
  {And justice to downtrodden ones.}
  {\textsuperscript{7} To Moses he made known his ways,}
  {His mighty deeds to Israel's sons.}
  \end
  \verse
  {\textsuperscript{8} The {\LORD} is merciful and kind,}
  {To anger slow, and full of grace.}
  {\textsuperscript{9} He will not constantly reprove,}
  {Or in his anger hide his face.}
  {\textsuperscript{10} He does not punish our misdeeds,}
  {Or give our sins their just reward.}
  {\textsuperscript{11} How great his love as high as heaven}
  {Towards all those who fear the {\LORD!}}
  \end
  \verse
  {\textsuperscript{12} As far as east is from the west,}
  {So far his love has borne away}
  {Our many sins and trespasses}
  {And all the guilt that on us lay.}
  {\textsuperscript{13} Just as a father loves his child,}
  {So God loves those who fear his name.}
  {\textsuperscript{14} For he remembers we are dust,}
  {And well he knows our feeble frame.}
  \end
  \verse
  {\textsuperscript{15} Each human life is like the grass,}
  {And like a meadow flower it grows.}
  {\textsuperscript{16} Its place will never be recalled}
  {Once over it the tempest blows.}
  {\textsuperscript{17} But everlasting is God's love}
  {For those who fear him, and their seed}
  {\textsuperscript{18} For those who keep his covenant,}
  {And carefully his precepts heed.}
  \end
  \verse
  {\textsuperscript{19} God's kingly rule is over all;}
  {In heaven he has set his throne.}
  {\textsuperscript{20} O you his angels, praise the {\LORD,}}
  {Strong ones by whom his will is done.}
  {\textsuperscript{21} O praise the {\LORD,} you heavenly hosts,}
  {His servants who perform his word.}
  {\textsuperscript{22} Praise God, his works throughout his realm,}
  {And you, my soul, O praise the {\LORD!}}
  \end
\end{psalm}

% ---

