\begin{song}{Christ Our Hope in Life and Death}
    \verse
    {What is our \m{F}hope in \m{Fsus}life and \m{F}death?}
    {\m{Fsus}Christ a\m{F}lone, Christ a\m{C}lone}
    {What \m{Csus}is our \m{F}only \m{C}confi\m{Dm}dence?}
    {\m{B{\flat}}That our \m{F}souls to \m{C}him be\m{F}long}
    {Who holds our \m{Am}days within his \m{Dm}hand?}
    {What comes, a\m{Gm}part from \m{F}his com\m{B{\flat}}mand?}
    {And what will \m{F}keep us \m{C7}to the \m{Dm}end?}
    {The \m{B{\flat}}love of \m{F}Christ, in \m{C7}which we \m{F}stand}
    \end
    \chorus
    {O \m{Dm}sing \m{B{\flat}}halle\m{F}lujah!}
    {Our \m{C}hope springs e\m{Dm}ternal}
    {\m{F}O \m{B{\flat}}sing halle\m{F}lujah!}
    {\m{B{\flat}}Now and \m{F}ever \m{C}we con\m{B{\flat}}fess}
    {Christ our \m{Dm7}hope in \m{C}life and \m{F}death}
    \end
    \verse
    {What truth can calm the troubled soul?}
    {God is good, God is good}
    {Where is his grace and goodness known?}
    {In our great Redeemer's blood}
    {Who holds our faith when fears arise?}
    {Who stands above the stormy trial?}
    {Who sends the waves that bring us nigh}
    {Unto the shore, the rock of Christ?}
    \end
    \verse
    {Unto the grave, what will we sing?}
    {``Christ, he lives; Christ, he lives!''}
    {And what reward will heaven bring?}
    {Everlasting life with him}
    {And we will rise to meet the Lord}
    {Then sin and death will be destroyed}
    {And we will feast in endless joy}
    {When Christ is ours for evermore}
    \end
    \cp{{\copyright}2020 Getty Music Publishing}
\end{song}

% ---

