\begin{song}{In Christ Alone}
    \verse
    {In \m{G}Christ \m{D}alone my \m{G}hope is \m{A}found,}
    {\m{D}He is my \m{G}light, my \m{A}strength, my \m{D}song;}
    {This \m{G}Corner\m{D}stone, this \m{G}solid \m{A}Ground,}
    {\m{D}Firm through the \m{G}fiercest \m{A}drought and \m{D}storm.}
    {\m{D}What Heights of \m{G}love, what \m{D}depths of \m{A}peace,}
    {When \m{D}fears are \m{G}stilled, when \m{Bm}strivings \m{A}cease!}
    {My \m{G}Comfor\m{D}ter, my \m{G}All in \m{A}All,}
    {\m{D}Here in the \m{G}love of \m{A}Christ I \m{D}stand.}
    \end
    \verse
    {In Christ alone! – who took on flesh,}
    {Fullness of God in helpless babe.}
    {This gift of love and righteousness,}
    {Scorned by the ones He came to save:}
    {Till on the cross as Jesus died,}
    {The wrath of God was satisfied-}
    {For every sin on His was laid;}
    {Here in the death of Christ I live.}
    \end
    \verse
    {There in the ground His body lay,}
    {Light of the world by darkness slain:}
    {Then bursting forth in glorious day}
    {Up from the grave He rose again!}
    {And as He stand in victory}
    {Sin's curse has lost its grip on me,}
    {For I am His and He is mine-}
    {Bought with the precious blood of Christ.}
    \end
    \verse
    {No guilt in life, no fear in death,}
    {This is the power of Christ in me;}
    {From life's first cry to final breath,}
    {Jesus commands my destiny.}
    {No power of Hell, no scheme of man,}
    {Can ever pluck me from His hand:}
    {Till He returns or calls me home,}
    {Here in the power of Christ I stand.}
    \end
\end{song}

% ---

