\begin{song}{Let Us Love And Sing And Wonder}
    \verse
    {Let us love and sing and wonder,}
    {Let us praise the Saviour's Name!}
    {He has hushed the law's loud thunder,}
    {He has quenched Mount Sinai's flame.}
    {He has washed us with His blood,}
    {He has brought us nigh to God.}
    \end
    \verse
    {Let us love the Lord Who bought us,}
    {Pitied us when enemies,}
    {Called us by His grace, and taught us,}
    {Gave us ears and gave us eyes:}
    {He has washed us with His blood,}
    {He presents our souls to God.}
    \end
    \verse
    {Let us sing, though fierce temptation}
    {Threaten hard to bear us down!}
    {For the Lord, our strong Salvation,}
    {Holds in view the conqueror's crown:}
    {He Who washed us with His blood}
    {Soon will bring us home to God.}
    \end
    \verse
    {Let us wonder; grace and justice}
    {Join and point to mercy's store;}
    {When through grace in Christ our trust is,}
    {Justice smiles and asks no more:}
    {He Who washed us with His blood}
    {Has secured our way to God.}
    \end
    \verse
    {Let us praise, and join the chorus}
    {Of the saints enthroned on high;}
    {Here they trusted Him before us,}
    {Now their praises fill the sky:}
    {``Thou hast washed us with Your blood;}
    {Thou art worthy, Lamb of God!''}
    \end
    \verse
    {Hark! The Name of Jesus, sounded}
    {Loud, from golden harps above!}
    {Lord, we blush, and are confounded,}
    {Faint our praises, cold our love!}
    {Wash our souls and songs with blood,}
    {For by Thee we come to God.}
    \end
\end{song}

% ---

