\begin{song}{Look Again}
    \verse
    {\m{Am}When our \m{F}joy in sal\m{C}vation \m{G}fades}
    {\m{Am}Days of \m{F}darkness draw \m{C}near}
    {\m{Am}When we \m{F}find ourselves \m{C}lost at \m{G}sea}
    {\m{Am}Drifting through \m{F}tides of \m{C}fear}
    \end
    \verse
    {When the emptiness mars our view}
    {Heaven's glories grow dim}
    {Caught in sadness we can't remove}
    {Keeps us from rest in Him}
    \end
    \chorus
    {\m{F}Look again to Calva\m{G}ry where des\m{Am}pair was overrun}
    {\m{F}Darkness will not always \m{G}be now The \m{Am}Light of Life Has \m{G}come}
    {\m{F}As you wait, wait patient\m{G}ly, cast your \m{Am}cares up\m{G}on the \m{F}One}
    {Who re\m{Am}deemed you and will \m{G}lead you safely \m{Am}home}
    \end
    \verse
    {When our hope of assurance fades}
    {Doubts and questions arise}
    {When we feel like we're all alone}
    {Far from our Saviour's side}
    \end
    \chorus
    {Look again to Calvary at your Saviour's arms stretched wide}
    {Hanging there for all to see under dark and heavy skies}
    {Hear Him cry in victory: ``It is finished!'' as He died}
    {He redeemed you, He will lead you safely home}
    \end
    \bridge
    {\m{Am}Halle\m{F}lujah! \m{C}Christ died for \m{G}me}
    {Hallelujah! Christ died for me}
    {Hallelujah! Christ died for me}
    {Hallelujah! Christ died for me}
    {Hallelujah! Christ rose again!}
    {Hallelujah! Christ rose again!}
    \end
    \bridge
    {He re\m{Am}deemed you! He won't \m{F}leave you!}
    {He Has \m{C}saved you! He will \m{G}keep you!}
    {He will \m{Am}guide you! Walk be\m{F}side you!}
    {He will \m{C}lead you safely \m{G}home!}
    \end
    \cp{{\copyright}2022 20schemes music, a division of 20schemes. From Hymns in Hard Places\\All rights reserved. www.20schemes.com\\CCLI \#7185774}
\end{song}

% ---

